Verifying Demonstrations

### 2019-09-12 paper/DB-anon-cred.tex
Adds comments that proofs are not using definitions
Changes to m challenges of length l
Instead of k challenges of length k.

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
    & \(c_1\rgets \bin^k, \dotsc, c_k\rgets \bin^k\)
    \\

@@

    \(s_k\gets \rho - c_k\alpha \pmod q\)
    &
    &
    \\

@@

    % null
    & \(\ProtoSendLeft{i}\)
    & \(i\rgets \{1, \dotsc, k\}\), start clock
    \\

@@

During one round, in the setup phase, the prover commits to a random nonce: 
more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
\(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates \(k\) challenges \(c_1\rgets \bin^k, \dotsc, c_k\rgets 
  \bin^k\) (bit strings of length \(k\)) and sends them to the prover.
The prover computes one response per challenge, \(s_1\gets \rho - c_1\alpha, 
  \dotsc, s_k\gets \rho - c_k\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier 
selects several challenges and the prover computes several responses --- but 
still only use \emph{one nonce}, \(\rho\).
This is needed for \ac{DBTF} resistance.
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

In the \ac{DB} phase, the prover notifies the verifier that he has computed 
\(s_1, \dotsc, s_k\).
The verifier chooses one of the challenges, \(i\), uniformly randomly and sends 
it as a challenge to the prover and starts measuring the time of flight.
The prover replies with \(s_i\).
The verifier stops the measurement and verifies that \(R = g^{s_i}A^{c_i}\) and 
that the time of flight was within \(t_{\max}\) (determined from the allowed 
  distance).

@@

The main difference between this protocol and the Schnorr protocol is that we 
have the prover compute responses for \(k\) different challenges, \(c_1, 
  \dotsc, c_k\).
However, in the authentication step, the verifier chooses only one of those 
challenges.
From the simulator's (and extractor's) perspective, there is no difference 
whether the verifier first chooses \(k\) and then chooses one of those \(k\) 
challenges, or if the verifier chooses the one challenge directly;
the distribution is the same, \(\frac{k}{n}\times \frac{1}{k} = \frac{1}{n}\).
Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
protocol with soundness error \(2^{-kn}\) still 
holds~\cite[\eg][]{OnSigmaProtocols}.
(We note that \(k\), which is also the length of the challenge bit string, must 
be logarithmic in the security parameter, \(\lambda\), for a malicious 
verifier.)

@@

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{k}+\frac{1}{q}\right)^n\), 
  where \(k, q\) are as in \cref{DB-Schnorr}.
\end{theorem}

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{k}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}

@@

\begin{theorem}[\acs*{DBDH} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q}\).
\end{theorem}

@@

\begin{theorem}[\acs*{DBTF} resistance]
  \dots
\end{theorem}

@@

The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
\(\UWBPR\) reply.
The verifier stops the clock and records the round-trip time~\(\delta t\).

@@

The verifier checks if \(R = \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and that 
the round-trip time \(\delta t < t_{\max}\) does not exceed the 
limit~\(t_{\max}\).

>>>>

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    & \(\ProtoSendLeft{c_1, \dotsc, c_m}\)
    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
    \\

@@

@@

@@

During one round, in the setup phase, the prover commits to a random nonce: 
more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
\(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates \(m\) challenges \(c_1\rgets \bin^l, \dotsc, c_m\rgets 
  \bin^l\) (bit strings of length \(l\)) and sends them to the prover.
The prover computes one response per challenge, \(s_1\gets \rho - c_1\alpha, 
  \dotsc, s_m\gets \rho - c_m\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier 
selects several challenges and the prover computes several responses --- but 
still only use \emph{one nonce}, \(\rho\).
This is needed for \ac{DBTF} resistance.
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

In the \ac{DB} phase, the prover notifies the verifier that he has computed 
\(s_1, \dotsc, s_m\).
The verifier chooses one of the challenges, \(i\), uniformly randomly and sends 
it as a challenge to the prover and starts measuring the time of flight.
The prover replies with \(s_i\).
The verifier stops the measurement and verifies that \(R = g^{s_i}A^{c_i}\) and 
that the time of flight was within \(t_{\max}\) (determined from the allowed 
  distance).

@@

The main difference between this protocol and the Schnorr protocol is that we 
have the prover compute responses for \(m\) different challenges, \(c_1, 
  \dotsc, c_m\).
However, in the authentication step, the verifier chooses only one of those 
challenges.
From the simulator's (and extractor's) perspective, there is no difference 
whether the verifier first chooses \(m\) and then chooses one of those \(m\) 
challenges, or if the verifier chooses the one challenge directly;
the distribution is the same, \(\frac{m}{n}\times \frac{1}{m} = \frac{1}{n}\).
Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
protocol with soundness error \(2^{-l n}\) still 
holds~\cite[\eg][]{OnSigmaProtocols}.
(We note that \(l\), which is also the length of the challenge bit string, must 
be logarithmic in the security parameter, \(\lambda\), for a malicious 
verifier.)

@@

\daniel{Still intuition, we need to use the formal definition of security 
  above.}
\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{m}+\frac{1}{q}\right)^n\), 
  where \(m, q\) are as in \cref{DB-Schnorr}.
\end{theorem}

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields success with probability 
    \(\frac{1}{m}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{m}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}

@@

\daniel{Still intuition, we need to use the formal definition of security 
  above.}
\begin{theorem}[\acs*{DBDH} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q^n}\).
\end{theorem}

@@

\daniel{Still intuition, we need the formal definition of security above.}
\begin{theorem}[\acs*{DBTF} resistance]
  \dots
\end{theorem}

@@

The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
\(\UWBPR\) reply.
The verifier stops the clock and records the round-trip time~\(\Delta t\).

@@

The verifier checks if \(R = \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and that 
the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
limit~\(t_{\max}\).
